MSF_Groupwork-NBA_shotlog

### 2016-10-09 MSFGroupwork-NBAHotHand.Rmd
creating a new DF for win/loss analysis

for (i in 1:nrow(df)) {
  df$HOME_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[5]
  df$AWAY_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[7]
}
```

```{r}
#combining columns for the analysis
library(reshape)
```

>>>>

for (i in 1:nrow(df)) {
  if (LOCATION[i]=="H") {df$HOME_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[5]
  df$AWAY_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[7]}
  if (LOCATION[i]=="A") {df$HOME_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[7] 
  df$AWAY_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[5]}
}

df$BLANK<-"" #for some reason cast function does not work with last column in dataframe, so I have created this BLANK column as I need to use AWAY_TEAM colum (it was a last column). 
```

```{r}
#combining columns for the analysis
library(reshape)
dfwl<- cast(df, GAME_ID1 + HOME_TEAM + AWAY_TEAM + W~ LOCATION)

summary(dfwl)
```
